---
title: "R Objects and Commands"
author: Montaque Reynolds 
weight: 5
subtitle: "3 types of R objects, vector, data frame, and matrix."
date: 2021-01-26
draft: false
links:
- icon: campground
  icon_pack: fas
  name: slides
  url: "/slides/05-why-netlify.html"
- icon: hiking
  icon_pack: fas
  name: activity
  url: "collection/day02/05-netlify/#activity"
---

## Vectors

Contains a set of values. These include `vec_num`, number vector and `vec_char` whwhich is a character vector. `c()` combines the elements of a vector and `<-` assigns a vector to a variable.

```{r}
vec_num <- c(1, 5, 6, 3)
vec_num
```

```{r}
vec_char <- c("apple", "banana", "mandarin", "melon")
vec_char
```

Once we have created a vector, we can extract its elements using the `[]` operator. For instance, you can extract the first element `[1]`, 

```{r}
vec_char <- c("apple", "banana", "mandarin", "melon")
vec_char[1]
```

or the first 3 elements `[1:3]`.

```{r}
vec_char[1:3]
```

## Some functions

### Arithmetic, Multiplication, Division, Subtraction

```{r}
vec_num2 <- vec_num + 2
vec_num3 <- vec_num / 2
vec_num4 <- vec_num * 4
vec_num5 <- vec_num - 1

vec_num

# Addition

vec_num2

# Division

vec_num3

# Multiplication

vec_num4

# Subtraction

vec_num5
```

## Comparing vectors using relational operators (returns `TRUE` or `FALSE`)

```{r}
vec_logi_gt5 <- vec_num >= 5
vec_logi_gt5
```

We can do this using the equality operator only on character vectors

```{r}
vec_logi_apple <- vec_char == "apple"
vec_logi_apple
```

We can also concatenate vector elements using `paste()`. 

```{r}
vec_char2 <- paste(c("red", "yellow", "orange", "green"), vec_char)
print(vec_char2)
```

We can also set names to the elements of a numeric vector

```{r}
names(vec_num) <- vec_char
print(vec_num)

```

## Data Frames

Data Frames combine multiple vectors to construct a data set. However, though vectors can be of different types, they can only be combined if they have the same lengths. 

```{r}
dat_fruit <- data.frame(name = vec_char, count = vec_num)
print(dat_fruit)
```

